Analysis

### 2020-02-25 reports/DRM_exp/analysis_DRM_exp1.Rmd
analysis based on review - code restructuring - compute correlation between given scene and prototype - prepare deepfeatures from conv3 and conv5

df2 <- readRDS(here("data/exp_DRM1/results_with_tgtdistances_200219.rds"))
```

@@

>>>>

df2 <- readRDS(here("data/exp_DRM1/results_with_tgtdistances_fc7_200219.rds"))
```

@@

## Correlation of distance from prototype with accuracy

```{r Correlation of distance from prototype with accuracy }

cor.test(~dist_to_proto+correct, df2)
